---
title: "Assignment2"
author: "Sarah Chopra"
date: "01/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Read CSV file

CSV file is a comma separated file with extension .csv. It contains data in table like format. With rows and columns, it is easier to handle the data. It is faster to sort and filter data from a table-like format. Also, if csv is combined with excel, we can also make graphs and visualize the data.
```{r pressure, echo=FALSE}
data <- read.csv("/Users/sarah/Desktop/DirectedStudies/assignment2iris.csv")
print(data)
plot(data)

```

```{r pressure, echo=FALSE}
df1 <-data.frame(y = c(ifelse((data$variety)=='Setosa',0,ifelse((data$variety)=='Virginica',1,0))),
                 x = (data$petal.width
                 ))


finalDataset <- dplyr::filter(df1, y==0|y==1)  ## "dplyr::" not required
plot(finalDataset$y~finalDataset$x)

```

```{r}
MLE_FUNC <- function(data){
  B0 <- data[1]
  B1 <- data[2]
  y <- finalDataset$y
  x1 <- finalDataset$x
  X <- B0 + B1 * x1 
  p <- exp(X) / (1 + exp(X))
  mle <- -sum(y * log(p) + (1 - y) * log(1 - p))
# mle <- sum(log(pi)*(y) + (1-(y))*log(1-pi))
  
  (mle)
}

MLE <- optim(c(0.1,0.1),
             fn = MLE_FUNC,
             control = list(trace = 0),
             hessian = FALSE)
MLE

print("Paramters")
print(MLE$par)
paste("MLE", MLE_FUNC(MLE$par))
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
